---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kochile

<!-- badges: start -->
<!-- badges: end -->

`kochile` is made to finish my essay.

## Installation

You can install the development version of `kochile` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chile0126/BBS/kochile")
```

## Example

Use `get_all_data ()` to import data that going to be used, which including `d0914`, `d1520`, `dkoh`, `site_bbs`, `site_bbs0914`, `site_bbs1520` and `site_koh`

```{r example, echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
library (googledrive)
library (googlesheets4)
library (kochile)
get_all_data ()
head (site_koh)
head (d1520) [1:6]
```

Use `get_distance ()` to calculate the distances between every site from BBS data and every site from KOH.
The output will be a matrix, unit = meter.

```{r dd, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
d <- get_distance ()
d[1:6, 1:6]
```

Use `buffer_from_koh (d)` to select BBS sites with `d` meters from KOH sites. Four lists will be exported: `ele`, `ks_result`, `site_bbs`, `plot`. 
`ele` is the elevations of KOH, entire BBS, and selected BBS sites. 
`ks_result` is the results of Kolmogorov-Smirnov test between KOH and different kinds of BBS site elevations
`site_bbs` is the site names of the entire and selected BBS sites.
`plot` contains four vectors of elevations. Can be plot by `plotrix::multhist()`.

```{r buffer, echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
library (magrittr)
library (plotrix)
BBS_5km <- buffer_from_koh (5000)
BBS_5km$ele$ele_koh %>% head ()

BBS_5km$ks_result$ks_0914

BBS_5km$site_bbs$sitekm_1520 %>% head ()

multhist (BBS_5km$plot, freq = F)
